---
title: "Primed Memory Retrieval: Conditional Accuracy"
author: "Abhilasha Kumar"
date: "November 16, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading and Formatting Data

```{r }
memory500 = read.csv("Compiled_Final500ms_CSV.csv", header = TRUE, sep = ",")
memory32 = read.csv("Compiled_Final32ms_CSV.csv", header = TRUE, sep = ",")
memory125 = read.csv("Compiled_Final125ms_CSV.csv", header = TRUE, sep = ",")
memory48 = read.csv("Compiled_Final48ms_CSV.csv", header = TRUE, sep = ",")
```

# Means Per Prime Condition

##32 ms

```{r }
library(dplyr)
prime_acc_32 = group_by(memory32, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)

prime_subject_acc_32 = group_by(memory32, Subject, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)
```

##48 ms

```{r}
library(dplyr)
prime_acc_48 = group_by(memory48, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)

prime_subject_acc_48 = group_by(memory48, Subject, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)
```

##500 ms
```{r}
library(dplyr)
prime_acc_500 = group_by(memory500, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)

prime_subject_acc_500 = group_by(memory500, Subject, PrimeCondition) %>%
  summarise_at(vars(ImmediateAccuracy, DelayedAccuracy,RTImmediate, RTDelayed), mean)
```


#ANOVAS

## 32 ms

### ANOVA for Immediate Recall

```{r}
prime_subject_acc_32$PrimeCondition = as.factor(prime_subject_acc_32$PrimeCondition)
prime_subject_acc_32$Subject = as.factor(prime_subject_acc_32$Subject)

immediate_aov_32 = aov(data = prime_subject_acc_32, 
                        ImmediateAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(immediate_aov_32)

options(contrasts = c('contr.sum', 'contr.poly'))
library(lsmeans)
library(multcomp)
imm_lsm = lsmeans::lsmeans(immediate_aov_32, c("PrimeCondition"))
prime_effect = cld(imm_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE)
library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```

### ANOVA for Delayed Recall
```{r}
delayed_aov_32 = aov(data = prime_subject_acc_32, 
                      DelayedAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(delayed_aov_32)
```

##48 ms

###ANOVA for Immediate Recall
```{r}
prime_subject_acc_48$PrimeCondition = as.factor(prime_subject_acc_48$PrimeCondition)
prime_subject_acc_48$Subject = as.factor(prime_subject_acc_48$Subject)

immediate_aov_48 = aov(data = prime_subject_acc_48, 
                        ImmediateAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(immediate_aov_48)

options(contrasts = c('contr.sum', 'contr.poly'))
library(lsmeans)
library(multcomp)
imm_lsm = lsmeans::lsmeans(immediate_aov_48, c("PrimeCondition"))
prime_effect = cld(imm_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE)
library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```


###ANOVA for Delayed Recall
```{r}
delayed_aov_48 = aov(data = prime_subject_acc_48, 
                      DelayedAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(delayed_aov_48)
```

##500 ms

###ANOVA for Immediate Recall
```{r}
prime_subject_acc_500$PrimeCondition = as.factor(prime_subject_acc_500$PrimeCondition)
prime_subject_acc_500$Subject = as.factor(prime_subject_acc_500$Subject)
immediate_aov_500 = aov(data = prime_subject_acc_500, 
                        ImmediateAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(immediate_aov_500)

options(contrasts = c('contr.sum', 'contr.poly'))
library(lsmeans)
library(multcomp)
imm_lsm = lsmeans::lsmeans(immediate_aov_500, c("PrimeCondition"))
prime_effect = cld(imm_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE)
library(knitr)
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```

###ANOVA for Delayed Recall
```{r}
delayed_aov_500 = aov(data = prime_subject_acc_500, 
                      DelayedAccuracy ~ PrimeCondition +
                                 Error(Subject/PrimeCondition))
summary(delayed_aov_500)
```

#Conditional Accuracy

##32 ms

##Organizing Data

```{r}
library(dplyr)
## overall delayed acc means split by imm acc (0/1)
cond_32 = group_by(memory32, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##per subject
cond_sub_32 = group_by(memory32, Subject, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##taking only correct immediate responses from this:
cond_sub_correct_32 = subset(cond_sub_32, cond_sub_32$ImmediateAccuracy == "1")

## Merging immediate and delayed into one file:

## now we have conditional delayed accuracies in cond_sub_correct_32
## and we have immediate accuracies in prime_subject_acc_32
## now we must combine the two files. 

colnames(cond_sub_correct_32) = c("Subject", "IA", "PrimeCondition", "Delayed")
colnames(prime_subject_acc_32) = c("Subject", "PrimeCondition", "Immediate", "DA",
                                   "RTImm", "RTdel")

final_combined_32 = merge(cond_sub_correct_32, prime_subject_acc_32, 
                       by = c("Subject", "PrimeCondition"))

# now we have immediate and delayed accuracy in wide format, i.e. side to side.
# We need to convert to long format

#first we remove uneccesary columns, i.e. IA and DA

final_combined_32 = final_combined_32[, -c(3,6,7,8)]

# converting to long

library(tidyr)
final_long_32 <- final_combined_32 %>%
  gather(Delay, Accuracy, Immediate, Delayed)
  

final_long_32 <- final_long_32[order(final_long_32$Subject),]
final_long_32$Delay = as.factor(as.character(final_long_32$Delay))
final_long_32$Subject = as.factor(as.character(final_long_32$Subject))
final_long_32$Accuracy = as.numeric(as.character(final_long_32$Accuracy))
```

###Conditional ANOVA

```{r}
final_aov_32 = aov(data = final_long_32, Accuracy ~ Delay*PrimeCondition + 
                  Error(Subject/(Delay*PrimeCondition)))
summary(final_aov_32)

library(multcomp)
library(knitr)
options(contrasts = c('contr.sum', 'contr.poly'))

conditional_lsm = lsmeans::lsmeans(final_aov_32, c("Delay", "PrimeCondition"))
prime_effect = cld(conditional_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE, by = "Delay")
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```

##48 ms

###Organizing Data

```{r}
library(dplyr)
## overall delayed acc means split by imm acc (0/1)
cond_48 = group_by(memory48, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##per subject
cond_sub_48 = group_by(memory48, Subject, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##taking only correct immediate responses from this:
cond_sub_correct_48 = subset(cond_sub_48, cond_sub_48$ImmediateAccuracy == "1")

#for 48 ms, S12 has 2 rows missing

cond_sub_correct_48[89,] = c("12",1,"Semantic", 0 )
cond_sub_correct_48[90,] = c("12",1,"UnSemantic", 0 )

##  Merging immediate and delayed into one file:

## now we have conditional delayed accuracies in cond_sub_correct_48
## and we have immediate accuracies in prime_subject_acc_48
## now we must combine the two files. 

colnames(cond_sub_correct_48) = c("Subject", "IA", "PrimeCondition", "Delayed")
colnames(prime_subject_acc_48) = c("Subject", "PrimeCondition", "Immediate", "DA",
                                   "RTImm", "RTDel")

final_combined_48 = merge(cond_sub_correct_48, prime_subject_acc_48, 
                       by = c("Subject", "PrimeCondition"))

# now we have immediate and delayed accuracy in wide format, i.e. side to side.
# We need to convert to long format

#first we remove uneccesary columns, i.e. IA and DA

final_combined_48 = final_combined_48[, -c(3,6,7,8)]

# converting to long

library(tidyr)
final_long_48 <- final_combined_48 %>%
  gather(Delay, Accuracy, Immediate, Delayed)
  

final_long_48 <- final_long_48[order(final_long_48$Subject),]
final_long_48$Delay = as.factor(as.character(final_long_48$Delay))
final_long_48$Subject = as.factor(as.character(final_long_48$Subject))
final_long_48$Accuracy = as.numeric(as.character(final_long_48$Accuracy))
```

###Conditional ANOVA
```{r}
final_aov_48 = aov(data = final_long_48, Accuracy ~ Delay*PrimeCondition + 
                  Error(Subject/(Delay*PrimeCondition)))
summary(final_aov_48)

library(multcomp)
library(knitr)
options(contrasts = c('contr.sum', 'contr.poly'))

conditional_lsm = lsmeans::lsmeans(final_aov_48, c("Delay", "PrimeCondition"))
prime_effect = cld(conditional_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE, by = "PrimeCondition")
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```

##500 ms

###Organizing Data
```{r}
library(dplyr)
## overall delayed acc means split by imm acc (0/1)
cond_500 = group_by(memory500, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##per subject
cond_sub_500 = group_by(memory500, Subject, ImmediateAccuracy, PrimeCondition) %>%
  summarise_at(vars(DelayedAccuracy), mean)
##taking only correct immediate responses from this:
cond_sub_correct_500 = subset(cond_sub_500, cond_sub_500$ImmediateAccuracy == "1")

#for 500 ms, S36 and S42 have one row each missing

cond_sub_correct_500[99,] = c("36",1,"Neutral", 0 )
cond_sub_correct_500[100,] = c("42",1,"Phonological", 0 )

##  Merging immediate and delayed into one file:

## now we have conditional delayed accuracies in cond_sub_correct_500
## and we have immediate accuracies in prime_subject_acc_500
## now we must combine the two files. 

colnames(cond_sub_correct_500) = c("Subject", "IA", "PrimeCondition", "Delayed")
colnames(prime_subject_acc_500) = c("Subject", "PrimeCondition", "Immediate", 
                                    "DA", "RTImm", "RTDel")

final_combined_500 = merge(cond_sub_correct_500, prime_subject_acc_500, 
                       by = c("Subject", "PrimeCondition"))

# now we have immediate and delayed accuracy in wide format, i.e. side to side.
# We need to convert to long format

#first we remove uneccesary columns, i.e. IA and DA

final_combined_500 = final_combined_500[, -c(3,6,7,8)]

# converting to long

library(tidyr)
final_long_500 <- final_combined_500 %>%
  gather(Delay, Accuracy, Immediate, Delayed)
  

final_long_500 <- final_long_500[order(final_long_500$Subject),]
final_long_500$Delay = as.factor(as.character(final_long_500$Delay))
final_long_500$Subject = as.factor(as.character(final_long_500$Subject))
final_long_500$Accuracy = as.numeric(as.character(final_long_500$Accuracy))
```

###Conditional ANOVA
```{r}
final_aov_500 = aov(data = final_long_500, Accuracy ~ Delay*PrimeCondition + 
                  Error(Subject/(Delay*PrimeCondition)))
summary(final_aov_500)

library(multcomp)
library(knitr)
options(contrasts = c('contr.sum', 'contr.poly'))

conditional_lsm = lsmeans::lsmeans(final_aov_500, c("Delay", "PrimeCondition"))
prime_effect = cld(conditional_lsm, alpha = 0.05, 
                adjust = "tukey", details = TRUE, by = "PrimeCondition")
kable(subset(prime_effect$comparisons,prime_effect$comparisons$p.value < 0.05 ))
```


#Figures

##32 ms
###Immediate Recall

```{r, fig}

library(Rmisc)
immediateagg_rmisc_32 = summarySE(prime_subject_acc_32, 
                      measurevar = "Immediate",
                      groupvars = c("PrimeCondition"))

## IMMEDIATE
library(ggplot2)
library(ggthemes)
immediateagg_rmisc_32 %>% mutate(PrimeCondition = factor(PrimeCondition, 
                                                 levels = unique(PrimeCondition),
                    labels = c("Identical", "Neutral", 
                               "Phonological", "Semantic", "Unrelated")))%>%
ggplot(aes(x = PrimeCondition, y = Immediate))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = Immediate - ci, ymax = Immediate + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") + 
  ggtitle("Immediate: Mean Accuracy by Prime Condition")
```

### Delayed Recall
```{r}
library(Rmisc)
delayedagg_rmisc_32 = summarySE(prime_subject_acc_32,
                      measurevar = "DA",
                      groupvars = c("PrimeCondition"))
#DELAYED
delayedagg_rmisc_32 %>% mutate(PrimeCondition = factor(PrimeCondition,
                                                 levels = unique(PrimeCondition),
                    labels = c("Identical", "Neutral",
                               "Phonological", "Semantic", "Unrelated")))%>%
ggplot(aes(x = PrimeCondition, y = DA))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = DA - ci, ymax = DA + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") +
  ggtitle("Delayed: Mean Accuracy by Prime Condition")
```
### Conditional Recall
```{r}
## PLOTTING INTERACTION
agg_final_combined_32 = group_by(final_long_32, Delay, PrimeCondition)%>%
  summarise_at(vars(Accuracy), mean)
library(Rmisc)
agg_rmisc_32 = summarySE(final_long_32,
                      measurevar = "Accuracy",
                      groupvars = c("Delay", "PrimeCondition"))

agg_rmisc_32 %>% mutate(PrimeCondition = factor(PrimeCondition,
                                                 levels = unique(PrimeCondition),
                    labels = c("Identical", "Neutral",
                               "Phonological", "Semantic", "Unrelated")))%>%
  ggplot(aes(x = PrimeCondition, y = Accuracy, fill = Delay))+
  geom_bar(stat = "identity", position = "dodge", width = 0.5)+
  geom_errorbar(aes(ymin = Accuracy - ci, ymax = Accuracy + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  scale_fill_solarized()+
  xlab("Prime Condition") + ylab("Mean Accuracy") +
  ggtitle("Mean Accuracy by Prime Condition and Delay")
```

## 48ms
### Immediate Recall
```{r}
library(Rmisc)
immediateagg_rmisc_48 = summarySE(prime_subject_acc_48,
                      measurevar = "Immediate",
                      groupvars = c("PrimeCondition"))

## IMMEDIATE
library(ggplot2)
library(ggthemes)
ggplot(immediateagg_rmisc_48, aes(x = PrimeCondition, y = Immediate))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = Immediate - ci, ymax = Immediate + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") +
  ggtitle("Immediate: Mean Accuracy by Prime Condition")

```

### Delayed Recall
```{r}
library(Rmisc)
delayedagg_rmisc_48 = summarySE(prime_subject_acc_48,
                      measurevar = "DA",
                      groupvars = c("PrimeCondition"))
#DELAYED
ggplot(delayedagg_rmisc_48, aes(x = PrimeCondition, y = DA))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = DA - ci, ymax = DA + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") +
  ggtitle("Delayed: Mean Accuracy by Prime Condition")
```

### Conditional Recall
```{r}
## PLOTTING INTERACTION
agg_final_combined_48 = group_by(final_long_48, Delay, PrimeCondition)%>%
  summarise_at(vars(Accuracy), mean)
library(Rmisc)
agg_rmisc_48 = summarySE(final_long_48,
                      measurevar = "Accuracy",
                      groupvars = c("Delay", "PrimeCondition"))

agg_rmisc_48 %>% mutate(PrimeCondition = factor(PrimeCondition,
                                                 levels = unique(PrimeCondition),
                    labels = c("Identical", "Neutral",
                               "Phonological", "Semantic", "Unrelated")))%>%
  ggplot(aes(x = PrimeCondition, y = Accuracy, fill = Delay))+
  geom_bar(stat = "identity", position = "dodge", width = 0.5)+
  geom_errorbar(aes(ymin = Accuracy - ci, ymax = Accuracy + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  scale_fill_solarized()+
  xlab("Prime Condition") + ylab("Mean Accuracy") +
  ggtitle("Mean Accuracy by Prime Condition and Delay")
```

## 500 ms

### Immediate Recall
```{r}
library(Rmisc)
immediateagg_rmisc_500 = summarySE(prime_subject_acc_500, 
                      measurevar = "Immediate",
                      groupvars = c("PrimeCondition"))

## IMMEDIATE
library(ggplot2)
library(ggthemes)
ggplot(immediateagg_rmisc_500, aes(x = PrimeCondition, y = Immediate))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = Immediate - ci, ymax = Immediate + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") + 
  ggtitle("Immediate: Mean Accuracy by Prime Condition")

```

### Delayed Recall 
```{r}
library(Rmisc)
delayedagg_rmisc_500 = summarySE(prime_subject_acc_500, 
                      measurevar = "DA",
                      groupvars = c("PrimeCondition"))
#DELAYED
ggplot(delayedagg_rmisc_500, aes(x = PrimeCondition, y = DA))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5, fill = "darkgreen")+
  geom_errorbar(aes(ymin = DA - ci, ymax = DA + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  xlab("Prime Condition") + ylab("Mean Accuracy") + 
  ggtitle("Delayed: Mean Accuracy by Prime Condition")

```
### Conditional Recall
```{r}
## PLOTTING INTERACTION
agg_final_combined_500 = group_by(final_long_500, Delay, PrimeCondition)%>%
  summarise_at(vars(Accuracy), mean)
library(Rmisc)
agg_rmisc_500 = summarySE(final_long_500, 
                      measurevar = "Accuracy",
                      groupvars = c("Delay", "PrimeCondition"))

agg_rmisc_500 %>% mutate(PrimeCondition = factor(PrimeCondition, 
                                                 levels = unique(PrimeCondition),
                    labels = c("Identical", "Neutral", 
                               "Phonological", "Semantic", "Unrelated")))%>%
  ggplot(aes(x = PrimeCondition, y = Accuracy, fill = Delay))+
 geom_bar(stat = "identity", position = "dodge", width = 0.5)+
  geom_errorbar(aes(ymin = Accuracy - ci, ymax = Accuracy + ci),
                width=.05, position=position_dodge(.5)) +
  theme_few()+
  scale_fill_solarized()+
  xlab("Prime Condition") + ylab("Mean Accuracy") + 
  ggtitle("Mean Accuracy by Prime Condition and Delay")

```
